Simulation study in rectangular domain

### 2024-05-05 R/simulation_study/rect/simulation_study_rect.Rmd
separate Rscript for simulation study

```{r global variables}
#number of batch
N_BATCH=20

@@

#sample theta and DistanceShore points in the domain
theta <- runif(n,-pi,pi);
DistanceShore <- runif(n,0.2,2);
samples=data.frame(theta=theta,DistanceShore=DistanceShore)

#define grid of values
theta_v <- seq(-pi,pi,length=30)
Dshore_v<- seq(0.2,2,length=30)
pr <- data.frame(theta=rep(theta_v,30),DistanceShore=rep(Dshore_v,rep(30,30)))

@@

#fit with bivariate splines te
m1 <- gam(y~te(theta,DistanceShore,k=SP_DF))

@@

#fit with bivariate splines te
m2 <- gam(y~te(theta,ExpShore,k=SP_DF))

@@

data_rect_hf_ne <- foreach(i=1:N_BATCH,.packages=c("progress","MASS","sf","foreach")) %dopar% {
  data=foreach (i=1:N_ID,.combine='rbind') %do% {

    res=sim_theta_CRCVM(ftau_constant,fomega,fnu_constant,log_sigma_obs=log(sigma_obs),v0,x0[i,],times_hf,land=domain,verbose=FALSE)

@@

crcvm_rect_hf_ne1<- foreach(k=1:N_BATCH,.packages=c("smoothSDE")) %do% {
  #estimation with tensor splines
  formulas <- list(mu1=~1,mu2=~1,tau=~s(ID,bs="re"),
                 nu=~s(ID,bs="re"),omega=~te(theta,ExpShore,k=SP_DF,bs="cs"))
  par0 <- c(0,0,1,1,0)
  m <- SDE$new(formulas = formulas,data = data_rect_hf_ne[[paste("BATCH",k,sep="")]],type = "RACVM",
                      response = c("y1","y2"),par0 = par0,fixpar=c("mu1","mu2"),
                      other_data=list("H"=H_hf))
  m$fit(method="BFGS")
  m 
}

@@

  #distance to shore
  Dshore=sqrt(normal[1]^2+normal[2]^2)
  if (Dshore<0.01) {
    return (100)
  }
  else {
    return (1/Dshore)
  }
}

@@

```{r plot sim te ExpSHore low error samples}

@@

crcvm_rect_hf_ne2<- foreach(k=1:N_BATCH,.packages=c("smoothSDE")) %do% {
  #estimation with tensor splines
  formulas <- list(mu1=~1,mu2=~1,tau=~s(ID,bs="re"),
                 nu=~s(ID,bs="re"),omega=~te(theta,DistanceShore,k=SP_DF,bs="cs"))
  par0 <- c(0,0,1,1,0)
  m <- SDE$new(formulas = formulas,data = data_rect_hf_ne[[paste("BATCH",k,sep="")]],type = "RACVM",
                      response = c("y1","y2"),par0 = par0,fixpar=c("mu1","mu2"),
                      other_data=list("H"=H_hf))
  m$fit(method="BFGS")
  m 
}

>>>>

```{r global variables}

@@

#sample theta and DistanceShore points in the domain
theta <- runif(n,-pi,pi);
DistanceShore <- runif(n,0.2,5);
samples=data.frame(theta=theta,DistanceShore=DistanceShore)

#define grid of values
theta_v <- seq(-pi,pi,length=30)
Dshore_v<- seq(0.2,5,length=30)
pr <- data.frame(theta=rep(theta_v,30),DistanceShore=rep(Dshore_v,rep(30,30)))

@@

#fit with bivariate splines te
m1 <- gam(y~te(theta,DistanceShore,k=SP_DF,bs="cs"),knots=list(theta=seq(-pi,pi,len=SP_DF),DistanceShore=seq(0.2,5,len=SP_DF)))

@@

#fit with bivariate splines te
m2 <- gam(y~te(theta,ExpShore,k=SP_DF,bs="cs"),knots=list(theta=seq(-pi,pi,len=SP_DF),ExpShore=seq(1/5,1/0.2,len=SP_DF)))

@@

data_rect_hf_ne <- foreach(k=1:N_BATCH,.packages=c("progress","MASS","sf","foreach","mgcv")) %dopar% {
  data=foreach (i=1:N_ID,.combine='rbind') %do% {

    res=sim_theta_CRCVM(ftau=ftau_constant,fomega=fomega_splines,fnu=fnu_constant,
                        log_sigma_obs=log(sigma_obs),v0=v0,x0=x0[i,],times=times_hf,land=domain,verbose=FALSE)

@@

crcvm_rect_hf_ne1<- foreach(k=1:N_BATCH,.packages=c("smoothSDE")) %do% {
  #estimation with tensor splines
  formulas <- list(mu1=~1,mu2=~1,tau=~s(ID,bs="re"),
                 nu=~s(ID,bs="re"),omega=~te(theta,ExpShore,k=SP_DF,bs="cs"))
  par0 <- c(0,0,1,1,0)
  knots=list("omega"=list(theta=seq(-pi,pi,len=SP_DF),ExpShore=seq(1/5,1/0.2,len=SP_DF)))

  m <- SDE$new(formulas = formulas,data = data_rect_hf_ne[[paste("BATCH",k,sep="")]],type = "RACVM",
                      response = c("y1","y2"),par0 = par0,fixpar=c("mu1","mu2"),
                      other_data=list("H"=H_hf),knots=knots)
  m$fit(method="BFGS")
  m 
}

@@

  #distance to shore
  Dshore=sqrt(normal[1]^2+normal[2]^2)
  if (Dshore<0.005) {
    return (2000)
  }
  else {
    return (1/Dshore)
  }
}

@@

```{r plot sim te ExpShore low error samples}

@@

crcvm_rect_hf_ne2<- foreach(k=1:N_BATCH,.packages=c("smoothSDE")) %do% {
  #estimation with tensor splines
  formulas <- list(mu1=~1,mu2=~1,tau=~s(ID,bs="re"),
                 nu=~s(ID,bs="re"),omega=~te(theta,DistanceShore,k=SP_DF,bs="cs"))
  par0 <- c(0,0,1,1,0)
  knots=list("omega"=list(theta=seq(-pi,pi,len=SP_DF),DistanceShore=seq(0.2,5,len=SP_DF)))

  m <- SDE$new(formulas = formulas,data = data_rect_hf_ne[[paste("BATCH",k,sep="")]],type = "RACVM",
                      response = c("y1","y2"),par0 = par0,fixpar=c("mu1","mu2"),
                      other_data=list("H"=H_hf),knots=knots)
  m$fit(method="BFGS")
  m 
}
